String Constraints with Regex-Counting and String-Length Solved Efficiently

### 2023-05-11 2023-1-19/sections/overview.tex
space adjustment
space ajustment
overview

\begin{figure}[ht]
  \centering
  \includegraphics[width = 0.95\textwidth]{sections/overview-cefa.pdf}
  \caption{CEFA for $(\Sigma \setminus a)^{\{1, 60\}} (\Sigma \setminus b)^{\{1, 60\}} (\Sigma \setminus c)^{\{0, 60\}}$, $\Sigma^* c^+$, and $|x|$}
  \label{fig:overview}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width = 0.95\textwidth]{sections/overview-cefa-product.pdf}
  \caption{$\aut_1 \cap \aut_2 \cap \aut_3$: Intersection of $\aut_1$, $\aut_2$, and $\aut_3$}
  \label{fig:overview:product}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width = 0.8\textwidth]{sections/overview-cefa-reduced.pdf}
  \caption{Reduced automaton $\cB$ and $\cC$}
  \label{fig:overview:product:reduced}
\end{figure}

@@

The wrong encoding of the backslash causes the soundness errors of z3str3re. Two backslashes are seen as two characters in the Smtlib2.6 standard, but z3str3re encodes them as one.

>>>>

\begin{figure}[ht]
\vspace{-3mm}
  \centering
  \includegraphics[width = 0.9\textwidth]{sections/overview-cefa.pdf}
  \caption{CEFA for $(\Sigma \setminus a)^{\{1, 60\}} (\Sigma \setminus b)^{\{1, 60\}} (\Sigma \setminus c)^{\{0, 60\}}$, $\Sigma^* c^+$, and $|x|$}
  \label{fig:overview}
\vspace{-5mm}
\end{figure}

@@

\begin{figure}[ht]
\vspace{-3mm}
  \centering
  \includegraphics[width = 0.9\textwidth]{sections/overview-cefa-product.pdf}
  \caption{$\aut_1 \cap \aut_2 \cap \aut_3$: Intersection of $\aut_1$, $\aut_2$, and $\aut_3$}
  \label{fig:overview:product}
\vspace{-6mm}
\end{figure}

@@

\begin{figure}[ht]
\vspace{-3mm}
  \centering
  \includegraphics[width = 0.8\textwidth]{sections/overview-cefa-reduced.pdf}
  \caption{Reduced automaton $\cB$ and $\cC$}
  \label{fig:overview:product:reduced}
\vspace{-3mm}
\end{figure}

@@

%The wrong encoding of the backslash causes the soundness errors of z3str3re. Two backslashes are seen as two characters in the Smtlib2.6 standard, but z3str3re encodes them as one.
